Big Ideas in Sports Analytics and Statistical Tools for their Investigation

### 2022-08-01 sports_analytics.Rmd
Small edits.

Note that Miami starts the play with an EPV of approximately 1.0 points.
This indicates their implied average points per possession. 
Chalmers's shot is worth 3 points, so the EPV of 1.276 points implies that the model estimate of the probability of Chalmers making this shot is 42.5\%. 
A breakthrough in this work is that this estimate is conditional on the locations of the other 9 players on the basketball court!

>>>>

Note that Miami starts the play with an EPV of approximately 1.0 points, which indicates their implied average points per possession. 
Chalmers' shot is worth 3 points, so the EPV of 1.276 points implies that the model estimate of the probability of Chalmers making this shot is 42.5\%. 
A breakthrough in this work is that this estimate is conditional on the locations of the other 9 players on the basketball court!
